---
title: "The Most Censored Wechat Public Accounts"
author: "curiositybits.cc"
date: "Updated on `r Sys.time()` GMT"
output:
  prettydoc::html_pretty:
    includes:
       after_body: footer.html
    theme: cayman
    highlight: github
       
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(DT)
library(readr)
library(ggplot2) 
library(ggthemes)
library(data.table)

byaccounts_wide <- read.csv("https://curiositybits.cc/files/byaccounts_wide.csv")
```

## Acknowledgement 

Data used for this visualization come from [Wechatscope API](https://wechatscope.jmsc.hku.hk/), a project of [JMSC@HKU](https://jmsc.hku.hk/)

## The most censored for violating internet laws (since 4/12/2018)

Showing public accounts that have at least 10 articles censored for violating internet laws. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
p1 <- ggplot(data = byaccounts_wide[byaccounts_wide$Violating_internet_laws>=10,], aes(x = reorder(nickname, Violating_internet_laws), y = Violating_internet_laws)) +
  geom_bar(aes(fill = Violating_internet_laws), stat = "identity") + 
  xlab("Accounts") + ylab("# of censored articles") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE)+
  theme_economist(base_size = 8, base_family = "SimSun",horizontal = TRUE, dkpanel = FALSE)+ scale_colour_economist()+
  theme(legend.position = "none")

p1
```

## The most self-censored (since 4/12/2018)

Showing top public accounts that have at least 20 articles deleted by the account owners.

```{r echo=FALSE, message=FALSE, warning=FALSE}
p2 <- ggplot(data = byaccounts_wide[byaccounts_wide$Deleted_by_the_account_owner>=20,], aes(x = reorder(nickname, Deleted_by_the_account_owner), y = Deleted_by_the_account_owner)) +
  geom_bar(aes(fill = Deleted_by_the_account_owner), stat = "identity") + 
  xlab("Accounts") + ylab("# of censored articles") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE)+
  theme_economist(base_size = 8, base_family = "SimSun",horizontal = TRUE, dkpanel = FALSE)+ scale_colour_economist()+
  theme(legend.position = "none")

p2
```

## The most censored through blocking the entire account (since 4/12/2018)

Showing top blocked public accounts that have at least 5 articles deleted.

```{r echo=FALSE, message=FALSE, warning=FALSE}
p3 <- ggplot(data = byaccounts_wide[byaccounts_wide$Account_blocked>=5,], aes(x = reorder(nickname, Account_blocked), y = Account_blocked)) +
  geom_bar(aes(fill = Account_blocked), stat = "identity") + 
  xlab("Accounts") + ylab("# of censored articles") +
  coord_flip(xlim = NULL, ylim = NULL, expand = TRUE, clip = "on") +
  geom_smooth(method = "lm", se = FALSE)+
  theme_economist(base_size = 8, base_family = "SimSun",horizontal = TRUE, dkpanel = FALSE)+ scale_colour_economist()+
  theme(legend.position = "none")

p3
```

## The entire dataset (since 4/12/2018)

```{r echo=FALSE, message=FALSE, warning=FALSE}
datatable(byaccounts_wide, options = list(pageLength = 50)) 
```

